A Study on Penguins: A Minimal Reproducible Example

### 2024-08-22 01_Example/Manuscript.qmd
Use {modelsummary} rather than {vtable}
Because {modelsummary} has fewer dependencies

```{r}
#| label: "tbl-descriptive-statistics"
#| echo: false
#| results: "asis"

# Call descriptive table with the vtable package
vtable::sumtable(data_clean, group = "species")

>>>>

```{r}
#| label: "descriptive-statistics"
#| echo: false
#| results: "asis"
#| tbl-cap: "Summary Statistics"

options(modelsummary_warning_latex_siunitx_preamble = FALSE) # Hide LaTeX compilation tips
modelsummary::datasummary_balance(formula = ~ species, data = data_clean, output = "latex", dinm = FALSE)
